### 2019-06-30 thesis-template/msc-thesis.tex
update

@@

Please note that all values in the test table where measured on following system:\\
\texttt{4 x 16-Core Gold 6142M 2.60GHz, 3072 GB RAM}.
\begin{table}
\small
\centering
\caption{Test Table:}
\begin{tabularx}{\columnwidth}{X|X|X|X}
\hline\hline
test name - Fig. \# & resolution ($x\times y\times\omega$) & runtime $[s]$ & memory consumption\\
\toprule
\enquote{drain} - \ref{ftle_base} & $101\times101\times64=652864$ & $179878$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times64=652864$ & $68787$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\
\hline 
 &  &  & \\ 
\hline 
\enquote{isotropic} - \ref{bow-ftle} & $51\times51\times32=163216$ & $1357$ & $8\times163216\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline
\enquote{rings} - \ref{bow-ftle} & $51\times51\times32=163216$ & $5761$ & $8\times163216\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{bow} - \ref{bow-ftle} & $51\times51\times32=163216$ & $6128$ & $8\times163216\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{star} - \ref{star-ftle} & $51\times51\times32=163216$ & $5815$ & $8\times163216\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times16=163216$ & $12308$ & $8\times163216\times 8\mathop{byte} +(101\times101 + 19\times16)\times8\mathop{byte}\approx11.754\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times32=326432$ & $24571$ & $8\times326432\times 8\mathop{byte} +(101\times101 + 19\times32)\times8\mathop{byte}\approx23.5\mathop{MB}$\\ 
\hline
\enquote{brain} - \ref{brain-ftle} & $128\times128\times64=1048576$ & $2427$ & $8\times166464\times 8\mathop{byte} +(128\times128 + 19\times64)\times8\mathop{byte}\approx75.5\mathop{MB}$\\
\hline
\enquote{heart} - \ref{heart-ftle} & $256\times256\times32=2097152$ & TODO & $8\times2097152\times 8\mathop{byte} +(256\times256 + 19\times64)\times8\mathop{byte}\approx151.0\mathop{MB}$\\
\hline 
\end{tabularx}
   \vskip 1pt
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusion and Future Work}
\label{chap:concl}
In this work, we have discussed the advantages and purposes of tensor field visualization in practical applications. Furthermore, we have presented a presented a technique to extract meaningful structures from tensor fields, which can, as a secondary purpose, also be used to visualize meaningful structures in $2D$ virtual geometrical scenes. To put it into context, we discussed its relations to vector field visualization techniques and other tensor field and light transport visualization methods. Also, we captured global illumination methods, since the proposed visualization method is derived from a global light transport method propagating intensities inside of a given Cartesian grid, consistent of cells defined by polar profiles (distributions), respectively. The intensities are redistributed stochastically by transmission profiles derived from the tensors in the field, used as windowing (weighting) functions. Based on this propagation algorithm, we can compute a FTLE-like field on the tensor field, as we obtain a final light distribution for each light source configuration (position and direction), which is considered as an energy-based flow map. In analogy to computing the FTLE field for vector fields, we analyze the gradient of the resulting flow map. The incongruity on the other hand, is that we need an additional inital direction on top of the inital position, because the tensors also dependent on the incoming direction, not as vectors only on their position. As a result, we obtain a $3D$ scalar field. This field can be visualized as volume (e.g. heatmap representation) to extract and segment ridges, i.e., key regions separating areas of correlating directional distributions. These ridges are in turn called Lagrangian coherent structures (LCS), which can be found in nature in , e.g., vortices in flow fields or moraines in glaciers. We designed comprehensive synthetic test tensor fields to evaluate our approach. Once we were convinced over its principal functionality, we applied the approach to some real data examples, namely DT-MRI scans of human brain and heart. Also we designed test runs to verify the physical plausibility of the results of the propagation scheme. The maps or fields we obtain, can make a statement about active regions in tensor fields, which do reveal the greatest tensor magnitude and anisotropy in combination.

A possible application would be mechanical component design, as we could segment ROIs exhibiting increased loads or in a greater scope even machine component design, which are produced in series. The invented technique could also aid geologist in analyzing stress in cross-sections of the earth to be able to predict earthquakes sufficiently soon enough.

One of the most relevant problems in visualization is incorporating uncertainty \cite{johnson}. Measurement, simulation or systematic (model) errors, boundary conditions or turbulences may introduce local uncertainty, which turns into global uncertainty through moving with the flow. This introduces propability density functions (PDFs) instead of certain single trajectories into the flow field. A real world example for uncertain vector fields is the measurement of blood flow and tissue velocity by phase contrast MRI, which yields an uncertain vector field due to the inherent noise in MRI scans. This uncertain vector field could be eventually visualized with our proposed technique. We just need to put it into the right context. The analogy to certain vector fields would be, that we could interpret our principal component ellipsoid as a propability density function and even replace it with such. The trajectories would be represented as propability distributions, which themselves are in turn propagated, just as we propagate our intensity profiles (distributions). As an outlook, we could apply our invented method to uncertain vector fields, which could be sampled in transmission profiles in discrete polar coordinates, just as we do in our work with the polar ellipsoids.

>>>>

When we consider the LTG method, we already stated its runtime behavior ($\mathcal{O}(\mathop{width^5}\mathop{steps^2})$), which makes parallelization libraries and hardware to compute the results in reasonable time. First, we tried to implement a GPU-based parallelization for the propagation scheme, which turned out not to work as expected, since the relative runtime gain was too low make a big difference. At this point, we choose to use OpenMP as we figured it is a much more suitable architecture employed here, which allows to perform the computation on a multiprocessor architecture provided by the Heidelberg University allowing to compute $64$ hardware threads at maximum. As we need fat fed, instruction-rich threads to have a high performance gain, we choose to parallelize only the outer loop of the LTG method (propagating final light distributions for each light source direction). Remark, that each thread requires its own memory, as an independent memory block is needed to perform the propagation in an individual propagator object of class propagator, in order to perform the computation in parallel.

@@

Please note that all values in the test table where measured on following system:\\
\texttt{4 x 16-Core Gold 6142M 2.60GHz, 3072 GB RAM}.
\begin{table}
\small
\centering
\caption{Test Table LTG:}
\begin{tabularx}{\columnwidth}{X|X|X|X}
\hline\hline
test name - Fig. \# & resolution ($x\times y\times\omega$) & runtime $[s]$ & memory consumption\\
\toprule
\enquote{drain} - \ref{ftle_base} & $101\times101\times64=652864$ & $179878$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times64=652864$ & $68787$ & $8\times652864\times 8\mathop{byte} +(101\times101 + 19\times64)\times8\mathop{byte}\approx47.02\mathop{MB}$\\
\hline 
 &  &  & \\ 
\hline 
\enquote{isotropic} - \ref{bow-ftle} & $51\times51\times3283232$ & $1357$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline
\enquote{rings} - \ref{bow-ftle} & $51\times51\times32=83232$ & $5761$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{bow} - \ref{bow-ftle} & $51\times51\times32=83232$ & $6128$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{star} - \ref{star-ftle} & $51\times51\times32=83232$ & $5815$ & $8\times83232\times 8\mathop{byte} +(51\times51 + 19\times32)\times8\mathop{byte}\approx5.998\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times16=163216$ & $12308$ & $8\times163216\times 8\mathop{byte} +(101\times101 + 19\times16)\times8\mathop{byte}\approx11.754\mathop{MB}$\\ 
\hline 
\enquote{inverse} - \ref{inverse-ftle} & $101\times101\times32=326432$ & $24571$ & $8\times326432\times 8\mathop{byte} +(101\times101 + 19\times32)\times8\mathop{byte}\approx23.5\mathop{MB}$\\ 
\hline
\enquote{brain} - \ref{brain-ftle} & $128\times128\times64=1048576$ & $2427$ & $8\times1048576\times 8\mathop{byte} +(128\times128 + 19\times64)\times8\mathop{byte}\approx75.5\mathop{MB}$\\
\hline
\enquote{heart} - \ref{heart-ftle} & $256\times256\times32=2097152$ & TODO & $8\times2097152\times 8\mathop{byte} +(256\times256 + 19\times32)\times8\mathop{byte}\approx151.0\mathop{MB}$\\
\hline 
\end{tabularx}
   \vskip 1pt
\end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Conclusion and Future Work}
\label{chap:concl}
In this work, we have discussed the advantages and purposes of tensor field visualization in practical applications. Furthermore, we have presented a presented a technique to extract meaningful structures from tensor fields, which can, as a secondary purpose, also be used to visualize meaningful structures in $2D$ virtual geometrical scenes. To put it into context, we discussed its relations to vector field visualization techniques and other tensor field and light transport visualization methods. Also, we captured global illumination methods, since the proposed visualization method is derived from a global light transport method propagating intensities inside of a given Cartesian grid, consistent of cells defined by polar profiles (distributions), respectively. The intensities are redistributed stochastically by transmission profiles derived from the tensors in the field, used as windowing (weighting) functions. Based on this propagation algorithm, we can compute a FTLE-like field on the tensor field, as we obtain a final light distribution for each light source configuration (position and direction), which is considered as an energy-based flow map. In analogy to the computation of the FTLE field for vector fields, we analyze the gradient of the resulting flow map. The incongruity on the other hand, is that we need an additional inital direction on top of the inital position, because the tensors also dependent on the incoming direction, not as vectors only on their location $x,y$. As a result, we obtain a $3D$ scalar field, which can be visualized as volume (e.g. heatmap representation) to extract and segment ridges, i.e., key regions separating areas of correlating directional distributions. These ridges are in turn called Lagrangian coherent structures (LCS), which can be found in nature in , e.g., vortices in flow fields or moraines in glaciers. We designed comprehensive synthetic test tensor fields to evaluate our approach. Once we were convinced over its principal functionality, we applied the approach to some real data examples, namely DT-MRI scans of human brain and heart. Also we designed test runs to verify the physical plausibility of the results of the propagation scheme. The maps or fields we obtain, can make a statement about active regions in tensor fields, which do reveal the greatest tensor magnitude and anisotropy in combination. The approach is positioned in interesting relation to the works of Zirr et al. \cite{zirr}, which perform their FTPD (FTLE-like) computation by random sampling of trajectories to compute light transport separatrices. They do not incorporate any transmission weighting functions, but instead blocker (obstacle) or reflecting geometry, which causes a FTLE response as well, as edges or mirrors cause light paths to cross each other chaotically in similar manner. Furthermore, the work of Hlawatsch et al. \cite{hlawatsch} obtains an FTLE field on tensor fields in similar style, as they use a coordinate map to sample their trajectories.

A possible application would be mechanical component design, as we could segment ROIs exhibiting increased loads or in a greater scope even machine component design, which are produced in series. The invented technique could also aid geologist in analyzing stress in cross-sections of the earth to be able to predict earthquakes sufficiently soon enough. In general one could measure vortices in directional distributions and hence tensor fields with a topological background (e.g. extracting separatrices of manifolds). One of the most relevant problems in visualization is incorporating uncertainty \cite{johnson}. Measurement, simulation or systematic (model) errors, boundary conditions or turbulences may introduce local uncertainty, which turns into global uncertainty through moving with the flow. This introduces propability density functions (PDFs) instead of certain single trajectories into the flow field. A real world example for uncertain vector fields is the measurement of blood flow and tissue velocity by phase contrast MRI, which yields an uncertain vector field due to the inherent noise in MRI scans. This uncertain vector field could be eventually visualized with our proposed technique. We just need to put it into the right context. The analogy to certain vector fields would be, that we could interpret our principal component ellipsoid as a propability density function and even replace it with such. The trajectories would be represented as propability distributions, which themselves are in turn propagated, just as we propagate our intensity profiles (distributions). As an outlook, we could apply our invented method to uncertain vector fields, which could be sampled in transmission profiles in discrete polar coordinates, just as we do in our work with the polar ellipsoids. Future works might include the previously mentioned application of the approach to uncertain vector fields or evaluating its applicability to real data in segmenting meaningful structures from engineering and medical data. Also we could imagine to implement a GPU parallelized version of the method to be able to propagate the intensities more efficiently, which would decrease the runtime in general. We can conclude, that tensor field visualization is becoming more and more important in scientific domains and that we invented a useful new tool in this context, which is worth of being investigated more precisely to reveal its potential in detecting meaningful information (key regions) and abstracting from redundancies in tensor fields.
